\documentclass[11pt,a4paper]{article}

% ==================== PACKAGES ====================
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage[margin=2.2cm]{geometry}
\setlength{\headheight}{22pt}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{fontawesome5}
\usepackage{tcolorbox}
\usepackage{tabularx}
\usepackage{colortbl}
\tcbuselibrary{skins, breakable}

% ==================== COLORS ====================
\definecolor{primary}{RGB}{0, 63, 92}
\definecolor{secondary}{RGB}{88, 80, 141}
\definecolor{accent}{RGB}{255, 166, 0}
\definecolor{success}{RGB}{46, 125, 50}
\definecolor{info}{RGB}{2, 136, 209}
\definecolor{lightbg}{RGB}{248, 249, 250}

% ==================== HYPERREF ====================
\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    urlcolor=info,
    pdftitle={Data Structures and Algorithms with C++},
    pdfauthor={Mahmoud Salem}
}

% ==================== HEADER/FOOTER ====================
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textcolor{primary}{\textbf{DSA with C++}}}
\fancyhead[R]{\small\textcolor{primary}{\textbf{Mahmoud Salem}}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{primary}\leaders\hrule height \headrulewidth\hfill}}

% ==================== SECTION FORMATTING ====================
\titleformat{\section}{\Large\bfseries\color{primary}}{}{0em}{}[\color{accent}\titlerule]
\titleformat{\subsection}{\large\bfseries\color{secondary}}{}{0em}{}
\titlespacing*{\section}{0pt}{18pt}{8pt}
\setcounter{secnumdepth}{0}

% ==================== CUSTOM BOXES ====================
\newtcolorbox{notebox}{
    colback=info!8, colframe=info,
    fonttitle=\bfseries, title={\faInfoCircle\ Note},
    rounded corners, boxrule=0.5pt
}

\newtcolorbox{tipbox}{
    colback=success!8, colframe=success,
    fonttitle=\bfseries, title={\faLightbulb\ Pro Tip},
    rounded corners, boxrule=0.5pt
}

\newtcolorbox{warningbox}{
    colback=accent!10, colframe=accent,
    fonttitle=\bfseries, title={\faExclamationTriangle\ Important},
    rounded corners, boxrule=0.5pt
}

\newtcolorbox{highlightbox}{
    colback=primary!5, colframe=primary,
    rounded corners, boxrule=0.5pt
}

% ==================== DOCUMENT ====================
\begin{document}

% ==================== TITLE PAGE ====================
\begin{titlepage}
\centering
\vspace*{1.5cm}

{\fontsize{28}{34}\selectfont\bfseries\color{primary} Data Structures \& Algorithms}\\[0.4cm]
{\fontsize{28}{34}\selectfont\bfseries\color{primary} with C++ (C++17)}

\vspace{0.8cm}
{\Large\color{secondary} A Complete Interview-Oriented Learning Roadmap}

\vspace{1.5cm}

\begin{highlightbox}
\centering
\begin{tabular}{rl}
\textbf{Instructor:} & Mahmoud Salem \\[0.2cm]
\textbf{Start Date:} & February 10, 2026 \\[0.2cm]
\textbf{Duration:} & 7 Months (56 Sessions) \\[0.2cm]
\textbf{Schedule:} & 2 Sessions per Week \\[0.2cm]
\textbf{Target:} & LeetCode Top 150 Problems \\[0.2cm]
\textbf{Price:} & \textcolor{success}{\textbf{\$150 USD}} \\
\end{tabular}
\end{highlightbox}

\vspace{1.5cm}

{\large\textit{Consistency} \textcolor{accent}{$\bullet$} \textit{Deep Understanding} \textcolor{accent}{$\bullet$} \textit{Confidence}}

\vspace{1.5cm}

\begin{tabular}{cc}
\colorbox{success!20}{\color{success}\faWhatsapp\ +20 101 162 0431} & 
\colorbox{info!20}{\color{info}\faEnvelope\ ma7moudalysalem@gmail.com}
\end{tabular}

\vspace{0.5cm}

\begin{tabular}{cc}
\faGithub\ \href{https://github.com/ma7moudalysalem}{github.com/ma7moudalysalem} &
\faLinkedin\ \href{https://linkedin.com/in/ma7moudalysalem}{linkedin.com/in/ma7moudalysalem}
\end{tabular}

\vfill
\end{titlepage}

% ==================== WELCOME ====================
\section{Welcome Message}

Welcome to the \textbf{Data Structures \& Algorithms with C++} course.

This course is designed to help you move from knowing how to write code to understanding how to \textit{think algorithmically}. You will learn how to analyze problems, break them down, and build correct and efficient solutions.

\begin{notebox}
This is not a crash course. It is a \textbf{structured, long-term journey} that rewards consistency and effort. Expect to dedicate 1-2 hours daily for practice outside of sessions.
\end{notebox}

% ==================== WHAT YOU WILL GAIN ====================
\section{What You Will Gain}

By the end of this course, you will be able to:

\begin{itemize}[leftmargin=1.5cm, itemsep=4pt]
    \item[\textcolor{success}{\faCheckCircle}] Solve \textbf{150+ carefully selected LeetCode problems}
    \item[\textcolor{success}{\faCheckCircle}] Identify common algorithmic patterns instantly
    \item[\textcolor{success}{\faCheckCircle}] Master \textbf{recursion, trees, graphs, and dynamic programming}
    \item[\textcolor{success}{\faCheckCircle}] Analyze \textbf{time and space complexity} confidently
    \item[\textcolor{success}{\faCheckCircle}] Approach technical interviews with \textbf{clarity and confidence}
    \item[\textcolor{success}{\faCheckCircle}] Write clean, optimized C++ code using modern STL
\end{itemize}

% ==================== METHODOLOGY ====================
\section{Teaching Methodology}

Each topic is delivered using a proven pedagogical structure:

\begin{itemize}[leftmargin=1.5cm, itemsep=4pt]
    \item[\textcolor{primary}{\faBook}] \textbf{Concept Sessions} --- Intuition, mental models, visuals, and core ideas
    \item[\textcolor{secondary}{\faCode}] \textbf{Problem-Solving Sessions} --- Live solving of interview-level problems
    \item[\textcolor{info}{\faLaptopCode}] \textbf{Hybrid Sessions} --- Explanation combined with guided practice
    \item[\textcolor{accent}{\faRedo}] \textbf{Review Sessions} --- Monthly consolidation and Q\&A
\end{itemize}

\begin{tipbox}
Special emphasis is placed on \textbf{recursion}, as it forms the foundation for trees, backtracking, and dynamic programming. Master recursion, and the rest becomes significantly easier.
\end{tipbox}

% ==================== STUDENT COMMITMENT ====================
\section{Student Commitment}

To benefit fully from this course, students are expected to:

\begin{itemize}[leftmargin=1.5cm, itemsep=3pt]
    \item Attend sessions regularly (2 sessions per week)
    \item Review session material after each class
    \item Attempt problems \textbf{independently} before viewing solutions
    \item Accept struggle as part of the learning process
\end{itemize}

\begin{warningbox}
\textbf{Progress comes from consistency, not speed.} Students who practice daily, even for short periods, outperform those who cram before sessions.
\end{warningbox}

\newpage

% ==================== CURRICULUM ====================
\section{Curriculum Overview}

\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabularx}{\textwidth}{|c|l|X|}
\hline
\rowcolor{primary!10}
\textbf{Month} & \textbf{Topic} & \textbf{Key Concepts} \\
\hline
1 & Arrays \& Strings & Big-O, Two Pointers, Sliding Window, STL \\
\rowcolor{lightbg}
2 & Linked Lists, Stacks \& Queues & Fast/Slow Pointers, Monotonic Stack \\
3 & Recursion \& Backtracking & Call Stack, Base Cases, Pruning \\
\rowcolor{lightbg}
4 & Trees \& BST & DFS, BFS, Tree Properties, BST Operations \\
5 & Heaps, Hashing \& Sorting & Priority Queues, Hash Tables, Custom Sort \\
\rowcolor{lightbg}
6 & Binary Search \& Graphs & Topological Sort, Union-Find, BFS/DFS \\
7 & Dynamic Programming & Memoization, Tabulation, Classic DP Patterns \\
\hline
\end{tabularx}
\end{center}

% ==================== DETAILED SCHEDULE ====================
\section{Detailed Session Schedule}

\subsection{Month 1: Foundations, Arrays \& Strings}

\begin{center}
\begin{tabular}{clll}
\toprule
\textbf{S} & \textbf{Type} & \textbf{Topic} & \textbf{LeetCode} \\
\midrule
1 & Concept & Course Overview + C++ Review & --- \\
2 & Concept & Time \& Space Complexity, STL & --- \\
3 & Concept & Array Problem Patterns & --- \\
4 & Solve & Two Pointers & 1, 26, 27, 88 \\
5 & Concept & Sliding Window Technique & --- \\
6 & Solve & Sliding Window Problems & 121, 209, 3 \\
7 & Concept & Strings \& Character Handling & --- \\
8 & Solve & String Problems & 125, 242, 49 \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Month 2: Linked Lists, Stack \& Queue}

\begin{center}
\begin{tabular}{clll}
\toprule
\textbf{S} & \textbf{Type} & \textbf{Topic} & \textbf{LeetCode} \\
\midrule
9 & Concept & Singly Linked Lists & --- \\
10 & Solve & Linked List Problems & 206, 21, 141 \\
11 & Concept & Fast \& Slow Pointer Technique & --- \\
12 & Solve & Cycle / Middle Problems & 142, 876, 234 \\
13 & Concept & Stack Fundamentals & --- \\
14 & Solve & Stack Applications & 20, 155, 496 \\
15 & Concept & Queue \& Deque & --- \\
16 & Solve & Queue Problems & 232, 933 \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Month 3: Recursion \& Backtracking}

\begin{notebox}
This month is \textbf{intentionally extended} with extra practice to ensure deep understanding. Recursion is the foundation for everything that follows.
\end{notebox}

\begin{center}
\begin{tabular}{clll}
\toprule
\textbf{S} & \textbf{Type} & \textbf{Topic} & \textbf{LeetCode} \\
\midrule
17 & Concept & Introduction to Recursion & --- \\
18 & Concept & Call Stack and Base Cases & --- \\
19 & Hybrid & Recursion on Arrays & 509, 70 \\
20 & Solve & Recursion Practice & 344, 206 \\
21 & Concept & Backtracking Fundamentals & --- \\
22 & Solve & Backtracking Problems & 46, 78 \\
23 & Hybrid & Recursion Tree Analysis & 22 \\
24 & Review & Full Recursion Review & Mixed \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Month 4: Trees \& Binary Search Trees}

\begin{center}
\begin{tabular}{clll}
\toprule
\textbf{S} & \textbf{Type} & \textbf{Topic} & \textbf{LeetCode} \\
\midrule
25 & Concept & Binary Tree Fundamentals & --- \\
26 & Solve & DFS Traversals & 94, 144, 145 \\
27 & Concept & BFS / Level Order Traversal & --- \\
28 & Solve & BFS Problems & 102, 199 \\
29 & Concept & Tree Properties & --- \\
30 & Solve & Height / Diameter & 104, 543 \\
31 & Concept & Binary Search Trees & --- \\
32 & Solve & BST Problems & 98, 230 \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Month 5: Heap, Hashing \& Sorting}

\begin{center}
\begin{tabular}{clll}
\toprule
\textbf{S} & \textbf{Type} & \textbf{Topic} & \textbf{LeetCode} \\
\midrule
33 & Concept & Heap and Priority Queue & --- \\
34 & Solve & Heap Problems & 215, 347 \\
35 & Concept & Hash Tables & --- \\
36 & Solve & Hashing Problems & 1, 217, 451 \\
37 & Concept & Sorting Algorithms & --- \\
38 & Solve & Sorting Problems & 912, 56 \\
39 & Hybrid & Custom Sorting & 179 \\
40 & Review & Monthly Review & Mixed \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Month 6: Binary Search \& Graphs}

\begin{center}
\begin{tabular}{clll}
\toprule
\textbf{S} & \textbf{Type} & \textbf{Topic} & \textbf{LeetCode} \\
\midrule
41 & Concept & Binary Search Fundamentals & --- \\
42 & Solve & Binary Search Problems & 704, 33 \\
43 & Concept & Graph Representation & --- \\
44 & Solve & DFS / BFS on Graphs & 200, 133 \\
45 & Concept & Topological Sorting & --- \\
46 & Solve & Topological Problems & 207, 210 \\
47 & Hybrid & Grid Graph Problems & 695 \\
48 & Review & Graph Review & Mixed \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Month 7: Dynamic Programming \& Final Review}

\begin{tipbox}
DP is the culmination of everything learned. If you mastered recursion in Month 3, DP will feel like a natural extension.
\end{tipbox}

\begin{center}
\begin{tabular}{clll}
\toprule
\textbf{S} & \textbf{Type} & \textbf{Topic} & \textbf{LeetCode} \\
\midrule
49 & Concept & DP Introduction & --- \\
50 & Solve & 1D Dynamic Programming & 70, 198 \\
51 & Concept & Knapsack Pattern & --- \\
52 & Solve & Knapsack Problems & 416 \\
53 & Concept & LIS and LCS & --- \\
54 & Solve & LIS / LCS Problems & 300, 1143 \\
55 & Solve & Advanced DP Problems & 62, 377 \\
56 & Final & \textbf{Full Course Revision} & Top 150 \\
\bottomrule
\end{tabular}
\end{center}

\newpage

% ==================== FAQ ====================
\section{Frequently Asked Questions}

\textbf{\textcolor{primary}{Do I need strong C++ knowledge before joining?}}\\
Basic familiarity with C++ is enough. The course includes a focused C++ review in the first week.

\vspace{0.4cm}

\textbf{\textcolor{primary}{Is this course suitable for beginners?}}\\
Yes, if you are committed. The difficulty increases gradually with continuous support.

\vspace{0.4cm}

\textbf{\textcolor{primary}{Will we solve all LeetCode Top 150 problems?}}\\
Yes. The curriculum systematically covers the entire list plus additional practice problems.

\vspace{0.4cm}

\textbf{\textcolor{primary}{What if I miss a session?}}\\
Recordings are available for 48 hours after each live session.

% ==================== ENROLLMENT ====================
\section{Enrollment Information}

\begin{center}
\begin{highlightbox}
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{rl}
\textbf{Course Fee:} & \textcolor{success}{\textbf{\$150 USD}} (one-time payment) \\
\textbf{Start Date:} & February 10, 2026 \\
\textbf{Duration:} & 7 Months (56 Sessions) \\
\textbf{Class Size:} & Maximum 30 Students \\
\textbf{Recordings:} & Available for 48 hours \\
\textbf{Certificate:} & Issued upon completion \\
\end{tabular}
\end{highlightbox}
\end{center}

\vspace{0.5cm}

\begin{center}
\textbf{\large Contact Information}\\[0.5cm]
\begin{tabular}{ll}
\faWhatsapp\ \textbf{WhatsApp:} & +20 101 162 0431 \\
\faEnvelope\ \textbf{Email:} & \href{mailto:ma7moudalysalem@gmail.com}{ma7moudalysalem@gmail.com} \\
\faGithub\ \textbf{GitHub:} & \href{https://github.com/ma7moudalysalem}{github.com/ma7moudalysalem} \\
\faLinkedin\ \textbf{LinkedIn:} & \href{https://linkedin.com/in/ma7moudalysalem}{linkedin.com/in/ma7moudalysalem} \\
\end{tabular}
\end{center}

% ==================== INSTRUCTOR ====================
\section{About the Instructor}

\textbf{Mahmoud Salem} is a Software \& Data Engineer with 4+ years of experience delivering enterprise-grade solutions across MENA and international markets.

\begin{itemize}[leftmargin=1.5cm, itemsep=2pt]
    \item[\textcolor{primary}{\faAngleRight}] .NET Core, ASP.NET, Microservices Architecture
    \item[\textcolor{primary}{\faAngleRight}] Azure Data Factory, Synapse Analytics, Cloud Platforms
    \item[\textcolor{primary}{\faAngleRight}] 500+ LeetCode problems solved
    \item[\textcolor{primary}{\faAngleRight}] ITI Graduate (Web Development \& BI)
    \item[\textcolor{primary}{\faAngleRight}] Experience with government digital transformation projects
\end{itemize}

% ==================== FINAL NOTE ====================
\vspace{1cm}
\begin{center}
\rule{0.6\textwidth}{0.4pt}\\[0.5cm]
\textit{``This course is designed for students who want \textbf{real improvement}, not shortcuts.}\\[0.2cm]
\textit{If you stay \textbf{consistent} and \textbf{trust the process},}\\
\textit{your problem-solving skills will improve \textbf{dramatically}.''}\\[0.5cm]
\textbf{--- Mahmoud Salem}
\end{center}

\end{document}
